---
title: "TC Exp3 MC2 Culled"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true
    toc_depth: 6
    code_folding: hide
    number_sections: false
    theme: cosmo

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

# Workspace Setup

```{r setup, message=FALSE, error=FALSE, warning=FALSE}
library(phyloseq)
library(reshape2)
library(tidyverse)
library(vegan)
library(HTSSIP)
library(ape)
library(CoDaSeq)
library(philr)
library(ggtree)
library(cowplot)
library(ggplot2)
library(viridis)
library(phytools)
```

# State Data
## Gas Data
```{r gas, fig.width=10,fig.height=8, dpi=300}
x<-read.csv(file='/Users/oliviaahern/Documents/R/Exp4/22Apr22/Exp4_Chemostat.csv',header=TRUE)
timec=x$Time..d.
mc1cO2c=x$CO2.MC1....
mc2cO2c=x$CO2.MC2....
mc3cO2c=x$CO2.MC3....
mc4cO2c=x$CO2.MC4....
mc5cO2c=x$CO2.MC5....
mc6cO2c=x$CO2.MC6....
mc1O2c=x$O2.MC1....
mc2O2c=x$O2.MC2....
mc3O2c=x$O2.MC3....
mc4O2c=x$O2.MC4....
mc5O2c=x$O2.MC5....
mc6O2c=x$O2.MC6....


x<-read.csv(file='/Users/oliviaahern/Documents/R/Exp4/22Apr22/Exp4_Batch.csv',header=TRUE)
time=x$Time..d.

mc1cO2=x$CO2.MC1....
mc2cO2=x$CO2.MC2....
mc3cO2=x$CO2.MC3....
mc4cO2=x$CO2.MC4....
mc5cO2=x$CO2.MC5....
mc6cO2=x$CO2.MC6....
mc1O2=x$O2.MC1....
mc2O2=x$O2.MC2....
mc3O2=x$O2.MC3....
mc4O2=x$O2.MC4....
mc5O2=x$O2.MC5....
mc6O2=x$O2.MC6....

par(mfrow=c(2,2),mar=c(5,5,1,1))
layout(matrix(c(1,2,2,3,4,4), nrow = 2, ncol = 3, byrow = TRUE))

plot(time,mc1O2, type='l',pch=21, col='gray70',ylim=c(20.8,21.2),
     xlab="Time (days)", lwd=1, cex.axis=1.5,cex.lab = 1.5,
     ylab="Oxygen (%)", yaxt='n')
axis(2, at=c(20.8, 21, 21.2), cex.axis=1.5)
lines(time, mc2O2, type='l', pch=21, col='#a44f9a')
lines(time, mc3O2, type='l', pch=21, col='#6870c8')
lines(time, mc4O2, type='l', pch=21, col='#56ae6c')
lines(time, mc5O2, type='l', pch=21, col='#af953c')
lines(time, mc6O2, type='l', pch=21, col='#ba4a4f')

plot(timec,mc1O2c, type='l',pch=21, col='gray70',ylim=c(20.5,21),
     xlab="Time (days)", lwd=1,cex.axis=1.5,cex.lab = 1.5,
     ylab="Oxygen (%)", yaxt="n")
axis(2, at=c(20.6, 20.8,21), cex.axis=1.5)
lines(timec, mc2O2c, type='l', pch=21, col='#a44f9a')
lines(timec, mc3O2c, type='l', pch=21, col='#6870c8')
lines(timec, mc4O2c, type='l', pch=21, col='#56ae6c')
lines(timec, mc5O2c, type='l', pch=21, col='#af953c')
lines(timec, mc6O2c, type='l', pch=21, col='#ba4a4f')

plot(time,mc1cO2, type='l',pch=21, col='gray70',ylim=c(0,0.2),
     xlab="Time (days)", lwd=1,cex.axis=1.5,cex.lab = 1.5,
     ylab="Carbon Dioxide (%)", yaxt='n')
axis(2, at=c(0,0.1,0.2), cex.axis=1.5)
lines(time, mc2cO2, type='l', pch=21, col='#a44f9a')
lines(time, mc3cO2, type='l', pch=21, col='#6870c8')
lines(time, mc4cO2, type='l', pch=21, col='#56ae6c')
lines(time, mc5cO2, type='l', pch=21, col='#af953c')
lines(time, mc6cO2, type='l', pch=21, col='#ba4a4f')

plot(timec,mc1cO2c, type='l',pch=21, col='gray70',ylim=c(0.18,0.3),
     xlab="Time (days)", lwd=1,cex.axis=1.5,cex.lab = 1.5,
     ylab="Carbon Dioxide (%)", yaxt="n")
axis(2, at=c(0.2, 0.25,0.3), cex.axis=1.5)
lines(timec, mc2cO2c, type='l', pch=21, col='#a44f9a')
lines(timec, mc3cO2c, type='l', pch=21, col='#6870c8')
lines(timec, mc4cO2c, type='l', pch=21, col='#56ae6c')
lines(timec, mc5cO2c, type='l', pch=21, col='#af953c')
lines(timec, mc6cO2c, type='l', pch=21, col='#ba4a4f')

```

## Atomic % 13C

```{r atomc2, fig.width=10,fig.height=5, dpi=300}

read=read.csv(file="/Users/oliviaahern/Documents/MBL_WHOI/Trophic_Cascades/Experiment4/SIP_Spins/atomic_C_30Aug22.csv",header=T)

read1=subset(read, B_C=="B")

MC1=subset(read1, MC=="MC1")
MC2=subset(read1, MC=="MC2")
MC3=subset(read1, MC=="MC3")
MC4=subset(read1, MC=="MC4")
MC5=subset(read1,MC=="MC5")
MC6=subset(read1,MC=="MC6")

read2=subset(read, B_C=="C")

MC1c=subset(read2, MC=="MC1")
MC2c=subset(read2, MC=="MC2")
MC3c=subset(read2, MC=="MC3")
MC4c=subset(read2, MC=="MC4")
MC5c=subset(read2,MC=="MC5")
MC6c=subset(read2,MC=="MC6")

{par(mar=c(5,5,1,1), mfrow=c(1,2))
plot(MC1$TP,MC1$mm_atomic_C, type='o',  ylim=c(0,10542.03827),pch=21,bg='gray70',
     xlab="Time (days)", ylab="Atomic %13C", cex=1.5, cex.lab=1.4)
lines(MC1$TP, MC2$mm_atomic_C, type="o", col="#a44f9a", bg="#a44f9a", pch=21,cex=1.5)
lines(MC1$TP, MC3$mm_atomic_C, type="o", col="#6870c8", bg="#6870c8", pch=21,cex=1.5)
lines(MC1$TP, MC4$mm_atomic_C, type="o", col="#56ae6c", bg="#56ae6c", pch=21,cex=1.5)
lines(MC1$TP, MC5$mm_atomic_C, type="o", col="#af953c", bg="#af953c", pch=21,cex=1.5)
lines(MC1$TP, MC6$mm_atomic_C, type="o", col="#ba4a4f", bg="#ba4a4f", pch=21,cex=1.5)
legend('topleft',legend=c("MC1-C12", "MC2-Met", "MC3-Eth", "MC4-Ace",
                          "MC5-Glu", "MC6-Xyl"), bty='n', pch =21,
       pt.bg=c("gray70", "#a44f9a", "#6870c8", "#56ae6c", "#af953c", "#ba4a4f"))


plot(MC1c$TP,MC1c$mm_atomic_C, type='o',  ylim=c(0,13424.45736),pch=21,bg='gray70',
     xlab="Time (days)", ylab="Atomic %13C", cex=1.5, cex.lab=1.4)
lines(MC1c$TP, MC2c$mm_atomic_C, type="o", col="#a44f9a", bg="#a44f9a", pch=21,cex=1.5)
lines(MC1c$TP, MC3c$mm_atomic_C, type="o", col="#6870c8", bg="#6870c8", pch=21,cex=1.5)
lines(MC1c$TP, MC4c$mm_atomic_C, type="o", col="#56ae6c", bg="#56ae6c", pch=21,cex=1.5)
lines(MC1c$TP, MC5c$mm_atomic_C, type="o", col="#af953c", bg="#af953c", pch=21,cex=1.5)
lines(MC1c$TP, MC6c$mm_atomic_C, type="o", col="#ba4a4f", bg="#ba4a4f", pch=21,cex=1.5)
legend('topleft',legend=c("MC1-C12", "MC2-Met", "MC3-Eth", "MC4-Ace",
                          "MC5-Glu", "MC6-Xyl"), bty='n', pch =21,
       pt.bg=c("gray70", "#a44f9a", "#6870c8", "#56ae6c", "#af953c", "#ba4a4f"))

}
```


## Atomic % 13C + POC

```{r atomc3, fig.width=6,fig.height=8, dpi=300}


{#par(mar=c(5,5,1,1), mfrow=c(2,2))
  layout(matrix(c(1,2,2,3,4,4), nrow = 2, ncol = 3, byrow = TRUE))
  
  plot(MC1$TP,MC1$Balanced_Atomic_.13C, type='o',  ylim=c(0,30),pch=21,bg='gray70',
       xlab="Time (days)", ylab="Atomic %13C", cex=1.2, cex.lab=1.2,
       yaxt='n')
  axis(2,at=c(0,10,20,30))
  lines(MC1$TP, MC2$Balanced_Atomic_.13C, type="o", col="#a44f9a", bg="#a44f9a", pch=21,cex=1.2)
  lines(MC1$TP, MC3$Balanced_Atomic_.13C, type="o", col="#6870c8", bg="#6870c8", pch=21,cex=1.2)
  lines(MC1$TP, MC4$Balanced_Atomic_.13C, type="o", col="#56ae6c", bg="#56ae6c", pch=21,cex=1.2)
  lines(MC1$TP, MC5$Balanced_Atomic_.13C, type="o", col="#af953c", bg="#af953c", pch=21,cex=1.2)
  lines(MC1$TP, MC6$Balanced_Atomic_.13C, type="o", col="#ba4a4f", bg="#ba4a4f", pch=21,cex=1.2)
 # legend('topleft',legend=c("MC1-C12", "MC2-Met", "MC3-Eth", "MC4-Ace",
  #                          "MC5-Glu", "MC6-Xyl"), bty='n', pch =21,
  #       pt.bg=c("gray70", "#a44f9a", "#6870c8", "#56ae6c", "#af953c", "#ba4a4f"))
  
  
  plot(MC1c$TP,MC1c$Balanced_Atomic_.13C, type='o',  ylim=c(0,30),pch=21,bg='gray70',
       xlab="Time (days)", ylab="Atomic %13C", cex=1.2, cex.lab=1.2,
       yaxt='n')
  axis(2,at=c(0,10,20,30))
  lines(MC1c$TP, MC2c$Balanced_Atomic_.13C, type="o", col="#a44f9a", bg="#a44f9a", pch=21,cex=1.2)
  lines(MC1c$TP, MC3c$Balanced_Atomic_.13C, type="o", col="#6870c8", bg="#6870c8", pch=21,cex=1.2)
  lines(MC1c$TP, MC4c$Balanced_Atomic_.13C, type="o", col="#56ae6c", bg="#56ae6c", pch=21,cex=1.2)
  lines(MC1c$TP, MC5c$Balanced_Atomic_.13C, type="o", col="#af953c", bg="#af953c", pch=21,cex=1.2)
  lines(MC1c$TP, MC6c$Balanced_Atomic_.13C, type="o", col="#ba4a4f", bg="#ba4a4f", pch=21,cex=1.2)
  #legend('topleft',legend=c("MC1-C12", "MC2-Met", "MC3-Eth", "MC4-Ace",
  #                          "MC5-Glu", "MC6-Xyl"), bty='n', pch =21,
   #      pt.bg=c("gray70", "#a44f9a", "#6870c8", "#56ae6c", "#af953c", "#ba4a4f"))

  
  plot(MC1$TP,MC1$POC.._M., type='o',  ylim=c(0,500),pch=21,bg='gray70',
       xlab="Time (days)", ylab="POC (uM)", cex=1.2, cex.lab=1.2,
       yaxt='n')
  axis(2,at=c(0,250,500))
  lines(MC1$TP, MC2$POC.._M., type="o", col="#a44f9a", bg="#a44f9a", pch=21,cex=1.2)
  lines(MC1$TP, MC3$POC.._M., type="o", col="#6870c8", bg="#6870c8", pch=21,cex=1.2)
  lines(MC1$TP, MC4$POC.._M., type="o", col="#56ae6c", bg="#56ae6c", pch=21,cex=1.2)
  lines(MC1$TP, MC5$POC.._M., type="o", col="#af953c", bg="#af953c", pch=21,cex=1.2)
  lines(MC1$TP, MC6$POC.._M., type="o", col="#ba4a4f", bg="#ba4a4f", pch=21,cex=1.2)

  
  plot(MC1c$TP,MC1c$POC.._M., type='o',  ylim=c(0,1100),pch=21,bg='gray70',
       xlab="Time (days)", ylab="POC (uM)", cex=1.2, cex.lab=1.2,
       yaxt='n')
  axis(2,at=c(0,500,1000))
  lines(MC1c$TP, MC2c$POC.._M., type="o", col="#a44f9a", bg="#a44f9a", pch=21,cex=1.2)
  lines(MC1c$TP, MC3c$POC.._M., type="o", col="#6870c8", bg="#6870c8", pch=21,cex=1.2)
  lines(MC1c$TP, MC4c$POC.._M., type="o", col="#56ae6c", bg="#56ae6c", pch=21,cex=1.2)
  lines(MC1c$TP, MC5c$POC.._M., type="o", col="#af953c", bg="#af953c", pch=21,cex=1.2)
  lines(MC1c$TP, MC6c$POC.._M., type="o", col="#ba4a4f", bg="#ba4a4f", pch=21,cex=1.2)
  
  
  }
```


# SIP Spins

## Batch 
```{r}
read=read.csv('/Users/oliviaahern/Documents/R/Exp4/25Aug22/qpcr_30Aug22.csv',header=T)
dim(read)

```




### Ribogreen Raw

#### MC1-C12
```{r ribo1a, fig.height=4, fig.width=8, dpi=300}
MC1_T2.5=subset(read, read$MC=="MC1" & TP =="2.5")
MC1_T3.5=subset(read, read$MC=="MC1" & TP =="3.5")
MC1_T4.5=subset(read, read$MC=="MC1" & TP =="4.5")



## Colors
# MC1 - gray 70
# MC2 #a44f9a
# MC3 #6870c8
# MC4 #56ae6c
# MC5 #af953c
# MC6 #ba4a4f

# C12-T2.5 and 3.5
par(mfrow=c(1,2))
plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
lines(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_RMAX,type="o", pch=22, bg="gray70")
lines(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
     ylab="Normalized RNA Conc.", bg='gray70',pch=23)
legend("topright", legend=c("MC1-C12-T2.5", "MC1-C12-T3.5","MC1-C12-T4.5"), pch=c(21,22,23),
       pt.bg=c("gray70", "gray70"), bty='n', cex=1)

plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
     ylim=c(0,3.75))
lines(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_conc,type="o", pch=22, bg="gray70")
lines(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
     ylab="Normalized RNA Conc.", bg='gray70',pch=23)
legend("topright", legend=c("MC1-C12-T2.5", "MC1-C12-T3.5","MC1-C12-T4.5"), pch=c(21,22,23),
       pt.bg=c("gray70", "gray70"), bty='n', cex=1)

```

#### MC1-C12 vs. MC2-Met



```{r ribo2a, fig.height=8, fig.width=8, dpi=300}

read=read.csv('/Users/oliviaahern/Documents/R/Exp4/25Aug22/qpcr_30Aug22.csv',header=T)
MC2_T2.5=subset(read, read$MC=="MC2" & TP =="2.5")
MC2_T3.5=subset(read, read$MC=="MC2" & TP =="3.5")
MC2_T4.5=subset(read, read$MC=="MC2" & TP =="4.5")


{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
lines(MC2_T2.5$Lueders_BD, MC2_T2.5$Ribo_RMAX,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
     ylim=c(0,3.2))
lines(MC2_T2.5$Lueders_BD, MC2_T2.5$Ribo_conc,type="o",  pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')


plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
lines(MC2_T3.5$Lueders_BD, MC2_T3.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,22),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
lines(MC2_T3.5$Lueders_BD, MC2_T3.5$Ribo_conc,type="o",  pch=22, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,22),
       pt.bg=c("gray70", "#a44f9a"), bty='n')



plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
lines(MC2_T4.5$Lueders_BD, MC2_T4.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a",
      col="#a44f9a")
legend("topleft", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,22),
       pt.bg=c("gray70", "#a44f9a"), bty='n')



plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
     ylim=c(0,4.6))
lines(MC2_T4.5$Lueders_BD, MC2_T4.5$Ribo_conc,type="o", pch=22, bg="#a44f9a",
      col="#a44f9a")
legend("topleft", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,22),
       pt.bg=c("gray70", "#a44f9a"), bty='n')



plot(MC2_T2.5$Lueders_BD, MC2_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
     ylab="Normalized RNA Conc.", bg='#a44f9a',pch=21, xlim=c(1.76,1.86),
     ylim=c(0,1), col="#a44f9a")
lines(MC2_T3.5$Lueders_BD, MC2_T3.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a",
      col="#a44f9a")
lines(MC2_T4.5$Lueders_BD, MC2_T4.5$Ribo_RMAX,type="o", pch=23, bg="#a44f9a",
      col="#a44f9a")
legend("topleft", legend=c("MC2-Met-T2.5","MC2-Met-T3.5", "MC2-Met-T4.5"), pch=c(21,22,23),
       pt.bg=c("#a44f9a", "#a44f9a"), bty='n')




plot(MC2_T2.5$Lueders_BD, MC2_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
     ylab="RNA Conc. (ng/uL)", bg='#a44f9a',pch=21, xlim=c(1.76,1.86),
     ylim=c(0,5), col="#a44f9a")
lines(MC2_T3.5$Lueders_BD, MC2_T3.5$Ribo_conc,type="o", pch=22, bg="#a44f9a",
      col="#a44f9a")
lines(MC2_T4.5$Lueders_BD, MC2_T4.5$Ribo_conc,type="o", pch=23, bg="#a44f9a",
      col="#a44f9a")
legend("topleft", legend=c("MC2-Met-T2.5","MC2-Met-T3.5", "MC2-Met-T4.5"), pch=c(21,22,23),
       pt.bg=c("#a44f9a", "#a44f9a"), bty='n')
}

```



#### MC1-C12 vs. MC3-Eth
```{r ribo3a, fig.height=8, fig.width=8, dpi=300}
# MC1-T2.5 and MC3-Eth-T2.5
read=read.csv('/Users/oliviaahern/Documents/R/Exp4/25Aug22/qpcr_30Aug22.csv',header=T)

MC3_T2.5=subset(read, read$MC=="MC3" & TP =="2.5")
MC3_T3.5=subset(read, read$MC=="MC3" & TP =="3.5")
MC3_T4.5=subset(read, read$MC=="MC3" & TP =="4.5")

{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC3_T2.5$Lueders_BD, MC3_T2.5$Ribo_RMAX,type="o", pch=21, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86), ylim=c(0,2.5))
  lines(MC3_T2.5$Lueders_BD, MC3_T2.5$Ribo_conc,type="o",  pch=21, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC3_T3.5$Lueders_BD, MC3_T3.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC3_T3.5$Lueders_BD, MC3_T3.5$Ribo_conc,type="o",  pch=22, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  
  plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC3_T4.5$Lueders_BD, MC3_T4.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8",
        col="#6870c8")
  legend("topleft", legend=c("MC1-C12-T4.5", "MC3-Eth-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  
  plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1.2))
  lines(MC3_T4.5$Lueders_BD, MC3_T4.5$Ribo_conc,type="o", pch=22, bg="#6870c8",
        col="#6870c8")
  legend("topleft", legend=c("MC1-C12-T4.5", "MC3-Eth-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  
  plot(MC3_T2.5$Lueders_BD, MC3_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='#6870c8',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1), col="#6870c8")
  lines(MC3_T3.5$Lueders_BD, MC3_T3.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8",
        col="#6870c8")
  lines(MC3_T4.5$Lueders_BD, MC3_T4.5$Ribo_RMAX,type="o", pch=23, bg="#6870c8",
        col="#6870c8")
  legend("topleft", legend=c("MC3-Eth-T2.5","MC3-Eth-T3.5", "MC3-Eth-T4.5"), pch=c(21,22,23),
         pt.bg=c("#6870c8", "#6870c8"), bty='n')
  
  
  
  
  plot(MC3_T2.5$Lueders_BD, MC3_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='#6870c8',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,5), col="#6870c8")
  lines(MC3_T3.5$Lueders_BD, MC3_T3.5$Ribo_conc,type="o", pch=22, bg="#6870c8",
        col="#6870c8")
  lines(MC3_T4.5$Lueders_BD, MC3_T4.5$Ribo_conc,type="o", pch=23, bg="#6870c8",
        col="#6870c8")
  legend("topleft", legend=c("MC3-Eth-T2.5","MC3-Eth-T3.5", "MC3-Eth-T4.5"), pch=c(21,22,23),
         pt.bg=c("#6870c8", "#6870c8"), bty='n')
}
```

#### MC1-C12 vs. MC4-Ace
```{r ribo4a, fig.height=8, fig.width=8, dpi=300}
######
# MC1 - T2.5 vs. MC4 - Ace 
MC4_T2.5=subset(read, read$MC=="MC4" & TP =="2.5")
MC4_T3.5=subset(read, read$MC=="MC4" & TP =="3.5")
MC4_T4.5=subset(read, read$MC=="MC4" & TP =="4.5")

{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC4_T2.5$Lueders_BD, MC4_T2.5$Ribo_RMAX,type="o", pch=21, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86), ylim=c(0,2.5))
  lines(MC4_T2.5$Lueders_BD, MC4_T2.5$Ribo_conc,type="o",  pch=21, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC4_T3.5$Lueders_BD, MC4_T3.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC4_T3.5$Lueders_BD, MC4_T3.5$Ribo_conc,type="o",  pch=22, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  
  plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC4_T4.5$Lueders_BD, MC4_T4.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c",
        col="#56ae6c")
  legend("topleft", legend=c("MC1-C12-T4.5", "MC4-Ace-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  
  plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,0.7))
  lines(MC4_T4.5$Lueders_BD, MC4_T4.5$Ribo_conc,type="o", pch=22, bg="#56ae6c",
        col="#56ae6c")
  legend("topleft", legend=c("MC1-C12-T4.5", "MC4-Ace-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  
  plot(MC4_T2.5$Lueders_BD, MC4_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='#56ae6c',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1), col="#56ae6c")
  lines(MC4_T3.5$Lueders_BD, MC4_T3.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c",
        col="#56ae6c")
  lines(MC4_T4.5$Lueders_BD, MC4_T4.5$Ribo_RMAX,type="o", pch=23, bg="#56ae6c",
        col="#56ae6c")
  legend("topleft", legend=c("MC4-Ace-T2.5","MC4-Ace-T3.5", "MC4-Ace-T4.5"), pch=c(21,22,23),
         pt.bg=c("#56ae6c", "#56ae6c"), bty='n')
  
  
  
  
  plot(MC4_T2.5$Lueders_BD, MC4_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='#56ae6c',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,5), col="#56ae6c")
  lines(MC4_T3.5$Lueders_BD, MC4_T3.5$Ribo_conc,type="o", pch=22, bg="#56ae6c",
        col="#56ae6c")
  lines(MC4_T4.5$Lueders_BD, MC4_T4.5$Ribo_conc,type="o", pch=23, bg="#56ae6c",
        col="#56ae6c")
  legend("topleft", legend=c("MC4-Ace-T2.5","MC4-Ace-T3.5", "MC4-Ace-T4.5"), pch=c(21,22,23),
         pt.bg=c("#56ae6c", "#56ae6c"), bty='n')
}

```

#### MC1-C12 vs. MC5-Glu
```{r ribo5a, fig.height=8, fig.width=8, dpi=300}
# MC1 vs MC5 
MC5_T2.5=subset(read, read$MC=="MC5" & TP =="2.5")
MC5_T3.5=subset(read, read$MC=="MC5" & TP =="3.5")
MC5_T4.5=subset(read, read$MC=="MC5" & TP =="4.5")
{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC5_T2.5$Lueders_BD, MC5_T2.5$Ribo_RMAX,type="o", pch=21, bg="#af953c", 
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86), ylim=c(0,2.5))
  lines(MC5_T2.5$Lueders_BD, MC5_T2.5$Ribo_conc,type="o",  pch=21, bg="#af953c", 
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  
  plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC5_T3.5$Lueders_BD, MC5_T3.5$Ribo_RMAX,type="o", pch=22, bg="#af953c", 
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC5_T3.5$Lueders_BD, MC5_T3.5$Ribo_conc,type="o",  pch=22, bg="#af953c", 
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  
  
  plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC5_T4.5$Lueders_BD, MC5_T4.5$Ribo_RMAX,type="o", pch=22, bg="#af953c",
        col="#af953c")
  legend("topleft", legend=c("MC1-C12-T4.5", "MC5-Glu-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  
  
  plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1))
  lines(MC5_T4.5$Lueders_BD, MC5_T4.5$Ribo_conc,type="o", pch=22, bg="#af953c",
        col="#af953c")
  legend("topleft", legend=c("MC1-C12-T4.5", "MC5-Glu-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  
  
  plot(MC5_T2.5$Lueders_BD, MC5_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='#af953c',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1), col="#af953c")
  lines(MC5_T3.5$Lueders_BD, MC5_T3.5$Ribo_RMAX,type="o", pch=22, bg="#af953c",
        col="#af953c")
  lines(MC5_T4.5$Lueders_BD, MC5_T4.5$Ribo_RMAX,type="o", pch=23, bg="#af953c",
        col="#af953c")
  legend("topleft", legend=c("MC5-Glu-T2.5","MC5-Glu-T3.5", "MC5-Glu-T4.5"), pch=c(21,22,23),
         pt.bg=c("#af953c", "#af953c"), bty='n')
  
  
  
  
  plot(MC5_T2.5$Lueders_BD, MC5_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='#af953c',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,2.5), col="#af953c")
  lines(MC5_T3.5$Lueders_BD, MC5_T3.5$Ribo_conc,type="o", pch=22, bg="#af953c",
        col="#af953c")
  lines(MC5_T4.5$Lueders_BD, MC5_T4.5$Ribo_conc,type="o", pch=23, bg="#af953c",
        col="#af953c")
  legend("topleft", legend=c("MC5-Glu-T2.5","MC5-Glu-T3.5", "MC5-Glu-T4.5"), pch=c(21,22,23),
         pt.bg=c("#af953c", "#af953c"), bty='n')
}

```

#### MC1-C12 vs. MC6-Xyl
```{r ribo6a, fig.height=8, fig.width=8, dpi=300}

MC6_T2.5=subset(read, read$MC=="MC6" & TP =="2.5")
MC6_T3.5=subset(read, read$MC=="MC6" & TP =="3.5")
MC6_T4.5=subset(read, read$MC=="MC6" & TP =="4.5")
{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC6_T2.5$Lueders_BD, MC6_T2.5$Ribo_RMAX,type="o", pch=21, bg="#ba4a4f", 
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  plot(MC1_T2.5$Lueders_BD, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86), ylim=c(0,2.5))
  lines(MC6_T2.5$Lueders_BD, MC6_T2.5$Ribo_conc,type="o",  pch=21, bg="#ba4a4f", 
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  
  plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC6_T3.5$Lueders_BD, MC6_T3.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f", 
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  plot(MC1_T3.5$Lueders_BD, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC6_T3.5$Lueders_BD, MC6_T3.5$Ribo_conc,type="o",  pch=22, bg="#ba4a4f", 
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  
  
  plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC6_T4.5$Lueders_BD, MC6_T4.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
        col="#ba4a4f")
  legend("topleft", legend=c("MC1-C12-T4.5", "MC6-Xyl-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  
  
  plot(MC1_T4.5$Lueders_BD, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1.5))
  lines(MC6_T4.5$Lueders_BD, MC6_T4.5$Ribo_conc,type="o", pch=22, bg="#ba4a4f",
        col="#ba4a4f")
  legend("topleft", legend=c("MC1-C12-T4.5", "MC6-Xyl-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  
  
  plot(MC6_T2.5$Lueders_BD, MC6_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders",
       ylab="Normalized RNA Conc.", bg='#ba4a4f',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1), col="#ba4a4f")
  lines(MC6_T3.5$Lueders_BD, MC6_T3.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
        col="#ba4a4f")
  lines(MC6_T4.5$Lueders_BD, MC6_T4.5$Ribo_RMAX,type="o", pch=23, bg="#ba4a4f",
        col="#ba4a4f")
  legend("topleft", legend=c("MC6-Xyl-T2.5","MC6-Xyl-T3.5", "MC6-Xyl-T4.5"), pch=c(21,22,23),
         pt.bg=c("#ba4a4f", "#ba4a4f"), bty='n')
  
  plot(MC6_T2.5$Lueders_BD, MC6_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Lueders",
       ylab="RNA Conc. (ng/uL)", bg='#ba4a4f',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,2.5), col="#ba4a4f")
  lines(MC6_T3.5$Lueders_BD, MC6_T3.5$Ribo_conc,type="o", pch=22, bg="#ba4a4f",
        col="#ba4a4f")
  lines(MC6_T4.5$Lueders_BD, MC6_T4.5$Ribo_conc,type="o", pch=23, bg="#ba4a4f",
        col="#ba4a4f")
  legend("topleft", legend=c("MC6-Xyl-T2.5","MC6-Xyl-T3.5", "MC6-Xyl-T4.5"), pch=c(21,22,23),
         pt.bg=c("#ba4a4f", "#ba4a4f"), bty='n')
}

```

### Ribo - Buckley 

#### MC1- C12

```{r ribo1b, fig.height=4, fig.width=8, dpi=300}
par(mfrow=c(1,2))
plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
lines(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", pch=22, bg="gray70")
lines(MC1_T4.5$Buckley, MC1_T4.5$Ribo_RMAX,type="o", bg='gray70',pch=23)
legend("topright", legend=c("MC1-C12-T2.5", "MC1-C12-T3.5","MC1-C12-T4.5"), pch=c(21,22,23),
       pt.bg=c("gray70", "gray70"), bty='n', cex=1)

plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
     ylim=c(0,3.75))
lines(MC1_T3.5$Buckley, MC1_T3.5$Ribo_conc,type="o", pch=22, bg="gray70")
lines(MC1_T4.5$Buckley, MC1_T4.5$Ribo_conc,type="o",  bg='gray70',pch=23)
legend("topright", legend=c("MC1-C12-T2.5", "MC1-C12-T3.5","MC1-C12-T4.5"), pch=c(21,22,23),
       pt.bg=c("gray70", "gray70"), bty='n', cex=1)
       
```       
#### MC1-C12- vs. MC2-Met
```{r ribo2b, fig.height=8, fig.width=8, dpi=300}

read=read.csv('/Users/oliviaahern/Documents/R/Exp4/25Aug22/qpcr_30Aug22.csv',header=T)
MC2_T2.5=subset(read, read$MC=="MC2" & TP =="2.5")
MC2_T3.5=subset(read, read$MC=="MC2" & TP =="3.5")
MC2_T4.5=subset(read, read$MC=="MC2" & TP =="4.5")


{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC2_T2.5$Buckley, MC2_T2.5$Ribo_RMAX,type="o", pch=21, bg="#a44f9a", 
        col="#a44f9a")
  legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#a44f9a"), bty='n')
  
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,3.2))
  lines(MC2_T2.5$Buckley, MC2_T2.5$Ribo_conc,type="o",  pch=21, bg="#a44f9a", 
        col="#a44f9a")
  legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#a44f9a"), bty='n')
  
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC2_T3.5$Buckley, MC2_T3.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a", 
        col="#a44f9a")
  legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#a44f9a"), bty='n')
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC2_T3.5$Buckley, MC2_T3.5$Ribo_conc,type="o",  pch=22, bg="#a44f9a", 
        col="#a44f9a")
  legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#a44f9a"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC2_T4.5$Buckley, MC2_T4.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a",
        col="#a44f9a")
  legend("topright", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#a44f9a"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,4.6))
  lines(MC2_T4.5$Buckley, MC2_T4.5$Ribo_conc,type="o", pch=22, bg="#a44f9a",
        col="#a44f9a")
  legend("topright", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#a44f9a"), bty='n')
  
  
  
  plot(MC2_T2.5$Buckley, MC2_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='#a44f9a',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1), col="#a44f9a")
  lines(MC2_T3.5$Buckley, MC2_T3.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a",
        col="#a44f9a")
  lines(MC2_T4.5$Buckley, MC2_T4.5$Ribo_RMAX,type="o", pch=23, bg="#a44f9a",
        col="#a44f9a")
  legend("topright", legend=c("MC2-Met-T2.5","MC2-Met-T3.5", "MC2-Met-T4.5"), pch=c(21,22,23),
         pt.bg=c("#a44f9a", "#a44f9a"), bty='n')
  
  
  
  
  plot(MC2_T2.5$Buckley, MC2_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='#a44f9a',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,5), col="#a44f9a")
  lines(MC2_T3.5$Buckley, MC2_T3.5$Ribo_conc,type="o", pch=22, bg="#a44f9a",
        col="#a44f9a")
  lines(MC2_T4.5$Buckley, MC2_T4.5$Ribo_conc,type="o", pch=23, bg="#a44f9a",
        col="#a44f9a")
  legend("topright", legend=c("MC2-Met-T2.5","MC2-Met-T3.5", "MC2-Met-T4.5"), pch=c(21,22,23),
         pt.bg=c("#a44f9a", "#a44f9a"), bty='n')
}

```



#### MC1-C12 vs. MC3-Eth
```{r ribo3b, fig.height=8, fig.width=8, dpi=300}
# MC1-T2.5 and MC3-Eth-T2.5
read=read.csv('/Users/oliviaahern/Documents/R/Exp4/25Aug22/qpcr_30Aug22.csv',header=T)

MC3_T2.5=subset(read, read$MC=="MC3" & TP =="2.5")
MC3_T3.5=subset(read, read$MC=="MC3" & TP =="3.5")
MC3_T4.5=subset(read, read$MC=="MC3" & TP =="4.5")

{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC3_T2.5$Buckley, MC3_T2.5$Ribo_RMAX,type="o", pch=21, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86), ylim=c(0,2.5))
  lines(MC3_T2.5$Buckley, MC3_T2.5$Ribo_conc,type="o",  pch=21, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC3_T3.5$Buckley, MC3_T3.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC3_T3.5$Buckley, MC3_T3.5$Ribo_conc,type="o",  pch=22, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC3_T4.5$Buckley, MC3_T4.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8",
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T4.5", "MC3-Eth-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1.2))
  lines(MC3_T4.5$Buckley, MC3_T4.5$Ribo_conc,type="o", pch=22, bg="#6870c8",
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T4.5", "MC3-Eth-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  
  plot(MC3_T2.5$Buckley, MC3_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='#6870c8',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1), col="#6870c8")
  lines(MC3_T3.5$Buckley, MC3_T3.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8",
        col="#6870c8")
  lines(MC3_T4.5$Buckley, MC3_T4.5$Ribo_RMAX,type="o", pch=23, bg="#6870c8",
        col="#6870c8")
  legend("topright", legend=c("MC3-Eth-T2.5","MC3-Eth-T3.5", "MC3-Eth-T4.5"), pch=c(21,22,23),
         pt.bg=c("#6870c8", "#6870c8"), bty='n')
  
  
  
  
  plot(MC3_T2.5$Buckley, MC3_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='#6870c8',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,5), col="#6870c8")
  lines(MC3_T3.5$Buckley, MC3_T3.5$Ribo_conc,type="o", pch=22, bg="#6870c8",
        col="#6870c8")
  lines(MC3_T4.5$Buckley, MC3_T4.5$Ribo_conc,type="o", pch=23, bg="#6870c8",
        col="#6870c8")
  legend("topright", legend=c("MC3-Eth-T2.5","MC3-Eth-T3.5", "MC3-Eth-T4.5"), pch=c(21,22,23),
         pt.bg=c("#6870c8", "#6870c8"), bty='n')
}
```

#### MC1-C12 vs. MC4-Ace
```{r ribo4b, fig.height=8, fig.width=8, dpi=300}
######
# MC1 - T2.5 vs. MC4 - Ace 
MC4_T2.5=subset(read, read$MC=="MC4" & TP =="2.5")
MC4_T3.5=subset(read, read$MC=="MC4" & TP =="3.5")
MC4_T4.5=subset(read, read$MC=="MC4" & TP =="4.5")

{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC4_T2.5$Buckley, MC4_T2.5$Ribo_RMAX,type="o", pch=21, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86), ylim=c(0,2.5))
  lines(MC4_T2.5$Buckley, MC4_T2.5$Ribo_conc,type="o",  pch=21, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC4_T3.5$Buckley, MC4_T3.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC4_T3.5$Buckley, MC4_T3.5$Ribo_conc,type="o",  pch=22, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC4_T4.5$Buckley, MC4_T4.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c",
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T4.5", "MC4-Ace-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,0.7))
  lines(MC4_T4.5$Buckley, MC4_T4.5$Ribo_conc,type="o", pch=22, bg="#56ae6c",
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T4.5", "MC4-Ace-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  
  plot(MC4_T2.5$Buckley, MC4_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='#56ae6c',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1), col="#56ae6c")
  lines(MC4_T3.5$Buckley, MC4_T3.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c",
        col="#56ae6c")
  lines(MC4_T4.5$Buckley, MC4_T4.5$Ribo_RMAX,type="o", pch=23, bg="#56ae6c",
        col="#56ae6c")
  legend("topright", legend=c("MC4-Ace-T2.5","MC4-Ace-T3.5", "MC4-Ace-T4.5"), pch=c(21,22,23),
         pt.bg=c("#56ae6c", "#56ae6c"), bty='n')
  
  
  
  
  plot(MC4_T2.5$Buckley, MC4_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='#56ae6c',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,5), col="#56ae6c")
  lines(MC4_T3.5$Buckley, MC4_T3.5$Ribo_conc,type="o", pch=22, bg="#56ae6c",
        col="#56ae6c")
  lines(MC4_T4.5$Buckley, MC4_T4.5$Ribo_conc,type="o", pch=23, bg="#56ae6c",
        col="#56ae6c")
  legend("topright", legend=c("MC4-Ace-T2.5","MC4-Ace-T3.5", "MC4-Ace-T4.5"), pch=c(21,22,23),
         pt.bg=c("#56ae6c", "#56ae6c"), bty='n')
}

```

#### MC1-C12 vs. MC5-Glu
```{r ribo5b, fig.height=8, fig.width=8, dpi=300}
# MC1 vs MC5 
MC5_T2.5=subset(read, read$MC=="MC5" & TP =="2.5")
MC5_T3.5=subset(read, read$MC=="MC5" & TP =="3.5")
MC5_T4.5=subset(read, read$MC=="MC5" & TP =="4.5")
{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC5_T2.5$Buckley, MC5_T2.5$Ribo_RMAX,type="o", pch=21, bg="#af953c", 
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86), ylim=c(0,2.5))
  lines(MC5_T2.5$Buckley, MC5_T2.5$Ribo_conc,type="o",  pch=21, bg="#af953c", 
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC5_T3.5$Buckley, MC5_T3.5$Ribo_RMAX,type="o", pch=22, bg="#af953c", 
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC5_T3.5$Buckley, MC5_T3.5$Ribo_conc,type="o",  pch=22, bg="#af953c", 
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC5_T4.5$Buckley, MC5_T4.5$Ribo_RMAX,type="o", pch=22, bg="#af953c",
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T4.5", "MC5-Glu-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1))
  lines(MC5_T4.5$Buckley, MC5_T4.5$Ribo_conc,type="o", pch=22, bg="#af953c",
        col="#af953c")
  legend("topright", legend=c("MC1-C12-T4.5", "MC5-Glu-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#af953c"), bty='n')
  
  
  
  plot(MC5_T2.5$Buckley, MC5_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='#af953c',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1), col="#af953c")
  lines(MC5_T3.5$Buckley, MC5_T3.5$Ribo_RMAX,type="o", pch=22, bg="#af953c",
        col="#af953c")
  lines(MC5_T4.5$Buckley, MC5_T4.5$Ribo_RMAX,type="o", pch=23, bg="#af953c",
        col="#af953c")
  legend("topright", legend=c("MC5-Glu-T2.5","MC5-Glu-T3.5", "MC5-Glu-T4.5"), pch=c(21,22,23),
         pt.bg=c("#af953c", "#af953c"), bty='n')
  
  
  
  
  plot(MC5_T2.5$Buckley, MC5_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='#af953c',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,2.5), col="#af953c")
  lines(MC5_T3.5$Buckley, MC5_T3.5$Ribo_conc,type="o", pch=22, bg="#af953c",
        col="#af953c")
  lines(MC5_T4.5$Buckley, MC5_T4.5$Ribo_conc,type="o", pch=23, bg="#af953c",
        col="#af953c")
  legend("topright", legend=c("MC5-Glu-T2.5","MC5-Glu-T3.5", "MC5-Glu-T4.5"), pch=c(21,22,23),
         pt.bg=c("#af953c", "#af953c"), bty='n')
}

```

#### MC1-C12 vs. MC6-Xyl
```{r ribo6b, fig.height=8, fig.width=8, dpi=300}

MC6_T2.5=subset(read, read$MC=="MC6" & TP =="2.5")
MC6_T3.5=subset(read, read$MC=="MC6" & TP =="3.5")
MC6_T4.5=subset(read, read$MC=="MC6" & TP =="4.5")
{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC6_T2.5$Buckley, MC6_T2.5$Ribo_RMAX,type="o", pch=21, bg="#ba4a4f", 
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86), ylim=c(0,2.5))
  lines(MC6_T2.5$Buckley, MC6_T2.5$Ribo_conc,type="o",  pch=21, bg="#ba4a4f", 
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC6_T3.5$Buckley, MC6_T3.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f", 
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC6_T3.5$Buckley, MC6_T3.5$Ribo_conc,type="o",  pch=22, bg="#ba4a4f", 
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.76,1.86))
  lines(MC6_T4.5$Buckley, MC6_T4.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T4.5", "MC6-Xyl-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1.5))
  lines(MC6_T4.5$Buckley, MC6_T4.5$Ribo_conc,type="o", pch=22, bg="#ba4a4f",
        col="#ba4a4f")
  legend("topright", legend=c("MC1-C12-T4.5", "MC6-Xyl-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#ba4a4f"), bty='n')
  
  
  
  plot(MC6_T2.5$Buckley, MC6_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='#ba4a4f',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,1), col="#ba4a4f")
  lines(MC6_T3.5$Buckley, MC6_T3.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
        col="#ba4a4f")
  lines(MC6_T4.5$Buckley, MC6_T4.5$Ribo_RMAX,type="o", pch=23, bg="#ba4a4f",
        col="#ba4a4f")
  legend("topright", legend=c("MC6-Xyl-T2.5","MC6-Xyl-T3.5", "MC6-Xyl-T4.5"), pch=c(21,22,23),
         pt.bg=c("#ba4a4f", "#ba4a4f"), bty='n')
  
  plot(MC6_T2.5$Buckley, MC6_T2.5$Ribo_conc,type="o", xlab="Buoyant Density - Buckley",
       ylab="RNA Conc. (ng/uL)", bg='#ba4a4f',pch=21, xlim=c(1.76,1.86),
       ylim=c(0,2.5), col="#ba4a4f")
  lines(MC6_T3.5$Buckley, MC6_T3.5$Ribo_conc,type="o", pch=22, bg="#ba4a4f",
        col="#ba4a4f")
  lines(MC6_T4.5$Buckley, MC6_T4.5$Ribo_conc,type="o", pch=23, bg="#ba4a4f",
        col="#ba4a4f")
  legend("topright", legend=c("MC6-Xyl-T2.5","MC6-Xyl-T3.5", "MC6-Xyl-T4.5"), pch=c(21,22,23),
         pt.bg=c("#ba4a4f", "#ba4a4f"), bty='n')
}

```

### Ribo Correct Both
#### MC1-C12 vs. MC2-Met
```{r ribo2, fig.height=8, fig.width=8, dpi=300}

read=read.csv('/Users/oliviaahern/Documents/R/Exp4/25Aug22/qpcr_30Aug22.csv',header=T)
MC2_T2.5=subset(read, read$MC=="MC2" & TP =="2.5")
MC2_T3.5=subset(read, read$MC=="MC2" & TP =="3.5")
MC2_T4.5=subset(read, read$MC=="MC2" & TP =="4.5")
MC1_T4.5=subset(read, read$MC=="MC1" & TP == "4.5")
MC1_T2.5=subset(read, read$MC=="MC1" & TP == "2.5")
MC1_T3.5=subset(read, read$MC=="MC1" & TP == "3.5")

{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
plot(MC1_T2.5$Corrected, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc. (ribogreen)", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC2_T2.5$Corrected, MC2_T2.5$Ribo_RMAX,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC2_T2.5$Buckley, MC2_T2.5$Ribo_RMAX,type="o",  pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')


plot(MC1_T3.5$Corrected, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC2_T3.5$Corrected, MC2_T3.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,22),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC2_T3.5$Buckley, MC2_T3.5$Ribo_RMAX,type="o",  pch=22, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,22),
       pt.bg=c("gray70", "#a44f9a"), bty='n')


plot(MC1_T4.5$Corrected, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc. ", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC2_T4.5$Corrected, MC2_T4.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,22),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC2_T4.5$Buckley, MC2_T4.5$Ribo_RMAX,type="o",  pch=22, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,22),
       pt.bg=c("gray70", "#a44f9a"), bty='n')


plot(MC2_T2.5$Corrected, MC2_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='#a44f9a',pch=21, xlim=c(1.735,1.85),
     col="#a44f9a")
lines(MC2_T3.5$Corrected, MC2_T3.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a", 
      col="#a44f9a")
lines(MC2_T4.5$Corrected, MC2_T4.5$Ribo_RMAX,type="o", pch=23, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC2-Met-T2.5", "MC2-Met-T3.5", "MC2-Met-T4.5"), pch=c(21,22,23),
       pt.bg=c("#a44f9a", "#a44f9a","#a44f9a"), bty='n')

plot(MC2_T2.5$Buckley, MC2_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='#a44f9a',pch=21, xlim=c(1.735,1.85),
     col="#a44f9a")
lines(MC2_T3.5$Buckley, MC2_T3.5$Ribo_RMAX,type="o", pch=22, bg="#a44f9a", 
      col="#a44f9a")
lines(MC2_T4.5$Buckley, MC2_T4.5$Ribo_RMAX,type="o", pch=23, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC2-Met-T2.5", "MC2-Met-T3.5", "MC2-Met-T4.5"), pch=c(21,22,23),
       pt.bg=c("#a44f9a", "#a44f9a","#a44f9a"), bty='n')

}

```



#### MC1-C12 vs. MC3-Eth
```{r ribo3, fig.height=8, fig.width=8, dpi=300}
# MC1-T2.5 and MC3-Eth-T2.5
read=read.csv('/Users/oliviaahern/Documents/R/Exp4/25Aug22/qpcr_30Aug22.csv',header=T)
MC3_T2.5=subset(read, read$MC=="MC3" & TP =="2.5")
MC3_T3.5=subset(read, read$MC=="MC3" & TP =="3.5")
MC3_T4.5=subset(read, read$MC=="MC3" & TP =="4.5")
MC1_T4.5=subset(read, read$MC=="MC1" & TP == "4.5")
MC1_T2.5=subset(read, read$MC=="MC1" & TP == "2.5")
MC1_T3.5=subset(read, read$MC=="MC1" & TP == "3.5")

{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Corrected, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
  lines(MC3_T2.5$Corrected, MC3_T2.5$Ribo_RMAX,type="o", pch=21, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
  lines(MC3_T2.5$Buckley, MC3_T2.5$Ribo_RMAX,type="o",  pch=21, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  plot(MC1_T3.5$Corrected, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
  lines(MC3_T3.5$Corrected, MC3_T3.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
  lines(MC3_T3.5$Buckley, MC3_T3.5$Ribo_RMAX,type="o",  pch=22, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  plot(MC1_T4.5$Corrected, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
  lines(MC3_T4.5$Corrected, MC3_T4.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T4.5", "MC3-Eth-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
  lines(MC3_T4.5$Buckley, MC3_T4.5$Ribo_RMAX,type="o",  pch=22, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC1-C12-T4.5", "MC3-Eth-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#6870c8"), bty='n')
  
  
  plot(MC3_T2.5$Corrected, MC3_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
       ylab="Normalized RNA Conc.", bg='#6870c8',pch=21, xlim=c(1.735,1.85),
       col="#6870c8")
  lines(MC3_T3.5$Corrected, MC3_T3.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8", 
        col="#6870c8")
  lines(MC3_T4.5$Corrected, MC3_T4.5$Ribo_RMAX,type="o", pch=23, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC3-Eth-T2.5", "MC3-Eth-T3.5", "MC3-Eth-T4.5"), pch=c(21,22,23),
         pt.bg=c("#6870c8", "#6870c8","#6870c8"), bty='n')
  
  plot(MC3_T2.5$Buckley, MC3_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc. ", bg='#6870c8',pch=21, xlim=c(1.735,1.85),
       col="#6870c8")
  lines(MC3_T3.5$Buckley, MC3_T3.5$Ribo_RMAX,type="o", pch=22, bg="#6870c8", 
        col="#6870c8")
  lines(MC3_T4.5$Buckley, MC3_T4.5$Ribo_RMAX,type="o", pch=23, bg="#6870c8", 
        col="#6870c8")
  legend("topright", legend=c("MC3-Eth-T2.5", "MC3-Eth-T3.5", "MC3-Eth-T4.5"), pch=c(21,22,23),
         pt.bg=c("#6870c8", "#6870c8","#6870c8"), bty='n')
  
}
```

#### MC1-C12 vs. MC4-Ace
```{r ribo4, fig.height=8, fig.width=8, dpi=300}
######
# MC1 - T2.5 vs. MC4 - Ace 
MC4_T2.5=subset(read, read$MC=="MC4" & TP =="2.5")
MC4_T3.5=subset(read, read$MC=="MC4" & TP =="3.5")
MC4_T4.5=subset(read, read$MC=="MC4" & TP =="4.5")


{
  par(mar=c(5,5,1,1),mfrow=c(4,2))
  plot(MC1_T2.5$Corrected, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.74,1.84))
  lines(MC4_T2.5$Corrected, MC4_T2.5$Ribo_RMAX,type="o", pch=21, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.74,1.84))
  lines(MC4_T2.5$Buckley, MC4_T2.5$Ribo_RMAX,type="o",  pch=21, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  plot(MC1_T3.5$Corrected, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.74,1.84))
  lines(MC4_T3.5$Corrected, MC4_T3.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.74,1.84))
  lines(MC4_T3.5$Buckley, MC4_T3.5$Ribo_RMAX,type="o",  pch=22, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  plot(MC1_T4.5$Corrected, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.74,1.84))
  lines(MC4_T4.5$Corrected, MC4_T4.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T4.5", "MC4-Ace-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  plot(MC1_T4.5$Buckley, MC1_T4.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.74,1.84))
  lines(MC4_T4.5$Buckley, MC4_T4.5$Ribo_RMAX,type="o",  pch=22, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC1-C12-T4.5", "MC4-Ace-T4.5"), pch=c(21,22),
         pt.bg=c("gray70", "#56ae6c"), bty='n')
  
  
  plot(MC4_T2.5$Corrected, MC4_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
       ylab="Normalized RNA Conc.", bg='#56ae6c',pch=21, xlim=c(1.74,1.84),
       col="#56ae6c")
  lines(MC4_T3.5$Corrected, MC4_T3.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c", 
        col="#56ae6c")
  lines(MC4_T4.5$Corrected, MC4_T4.5$Ribo_RMAX,type="o", pch=23, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC4-Ace-T2.5", "MC4-Ace-T3.5", "MC4-Ace-T4.5"), pch=c(21,22,23),
         pt.bg=c("#56ae6c", "#56ae6c","#56ae6c"), bty='n')
  
  plot(MC4_T2.5$Buckley, MC4_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
       ylab="Normalized RNA Conc.", bg='#56ae6c',pch=21, xlim=c(1.74,1.84),
       col="#56ae6c")
  lines(MC4_T3.5$Buckley, MC4_T3.5$Ribo_RMAX,type="o", pch=22, bg="#56ae6c", 
        col="#56ae6c")
  lines(MC4_T4.5$Buckley, MC4_T4.5$Ribo_RMAX,type="o", pch=23, bg="#56ae6c", 
        col="#56ae6c")
  legend("topright", legend=c("MC4-Ace-T2.5", "MC4-Ace-T3.5", "MC4-Ace-T4.5"), pch=c(21,22,23),
         pt.bg=c("#56ae6c", "#56ae6c","#56ae6c"), bty='n')
  
}

```

#### MC1-C12 vs. MC5-Glu
```{r ribo5, fig.height=8, fig.width=8, dpi=300}
# MC1 vs MC5 
MC5_T2.5=subset(read, read$MC=="MC5" & TP =="2.5")
MC5_T3.5=subset(read, read$MC=="MC5" & TP =="3.5")
MC5_T4.5=subset(read, read$MC=="MC5" & TP =="4.5")


{
par(mar=c(5,5,1,1),mfrow=c(3,2))

plot(MC1_T2.5$Corrected, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.7, 1.83))
lines(MC5_T2.5$Corrected, MC5_T2.5$Ribo_RMAX,type="o", pch=21, bg="#af953c",
      col="#af953c")
legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.7, 1.83))
lines(MC5_T2.5$Buckley, MC5_T2.5$Ribo_RMAX,type="o", pch=21, bg="#af953c",
      col="#af953c")
legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)


plot(MC1_T3.5$Corrected, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.7, 1.83))
lines(MC5_T3.5$Corrected, MC5_T3.5$Ribo_RMAX,type="o", pch=21, bg="#af953c",
      col="#af953c")
legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.7, 1.83))
lines(MC5_T3.5$Buckley, MC5_T3.5$Ribo_RMAX,type="o", pch=21, bg="#af953c",
      col="#af953c")
legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)


plot(MC5_T2.5$Corrected, MC5_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='#af953c',pch=21, xlim=c(1.7, 1.83),
     col="#af953c")
lines(MC5_T3.5$Corrected, MC5_T3.5$Ribo_RMAX,type="o", pch=22, bg="#af953c",
      col="#af953c")
legend("topright", legend=c("MC5-Glu-T2.5", "MC5-Glu-T3.5"), pch=c(21,22),
       pt.bg=c("#af953c", "#af953c"), bty='n', cex=0.9)

plot(MC5_T2.5$Buckley, MC5_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='#af953c',pch=21, xlim=c(1.7, 1.83),
     col="#af953c")
lines(MC5_T3.5$Buckley, MC5_T3.5$Ribo_RMAX,type="o", pch=22, bg="#af953c",
      col="#af953c")
legend("topright", legend=c("MC5-Glu-T2.5", "MC5-Glu-T3.5"), pch=c(21,22),
       pt.bg=c("#af953c", "#af953c"), bty='n', cex=0.9)

}
```

#### MC1-C12 vs. MC6-Xyl
```{r ribo6, fig.height=8, fig.width=8, dpi=300}

MC6_T2.5=subset(read, read$MC=="MC6" & TP =="2.5")
MC6_T3.5=subset(read, read$MC=="MC6" & TP =="3.5")
MC6_T4.5=subset(read, read$MC=="MC6" & TP =="4.5")

{
par(mar=c(5,5,1,1),mfrow=c(3,2))
plot(MC1_T2.5$Corrected, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.7, 1.83))
lines(MC6_T2.5$Corrected, MC6_T2.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.7, 1.83))
lines(MC6_T2.5$Buckley, MC6_T2.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)


plot(MC1_T3.5$Corrected, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.7, 1.84))
lines(MC6_T3.5$Corrected, MC6_T3.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,22),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.75, 1.85))
lines(MC6_T3.5$Buckley, MC6_T3.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,22),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)

plot(MC6_T2.5$Corrected, MC6_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='#ba4a4f',pch=21, xlim=c(1.7, 1.84),
     col="#ba4a4f")
lines(MC6_T3.5$Corrected, MC6_T3.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
      col="#ba4a4f")
legend("topright", legend=c("MC6-Xyl-T2.5", "MC6-Xyl-T3.5"), pch=c(21,22),
       pt.bg=c("#ba4a4f", "#ba4a4f"), bty='n', cex=0.9)

plot(MC6_T2.5$Buckley, MC6_T2.5$Ribo_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='#ba4a4f',pch=21, xlim=c(1.75, 1.85), 
     col="#ba4a4f")
lines(MC6_T3.5$Buckley, MC6_T3.5$Ribo_RMAX,type="o", pch=22, bg="#ba4a4f",
      col="#ba4a4f")
legend("topright", legend=c("MC6-Xyl-T2.5", "MC6-Xyl-T3.5"), pch=c(21,22),
       pt.bg=c("#ba4a4f", "#ba4a4f"), bty='n', cex=0.9)


}
```


### qRT PCR
#### C12 T2.5, 3.5, & 4.5
```{r qpcr_a, fig.height=7,fig.width=8, dpi=300}

{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected", xlim=c(1.7, 1.83),
     ylab="Normalized RNA Conc", bg='gray70',pch=21)
lines(MC1_T3.5$Corrected, MC1_T3.5$qPCR_RMAX,type="o", pch=22, bg="gray70", 
      col="black")
lines(MC1_T4.5$Corrected, MC1_T4.5$qPCR_RMAX,type="o", pch=23, bg="gray70", 
      col="black")
legend("topright", legend=c("MC1-C12-T2.5", "MC1-C12-T3.5", "MC1-C12-T4.5"), pch=c(21,22,23),
       pt.bg="gray70", bty='n')

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley", xlim=c(1.73, 1.85),
     ylab="Normalized RNA Conc", bg='gray70',pch=21)
lines(MC1_T3.5$Buckley, MC1_T3.5$qPCR_RMAX,type="o", pch=22, bg="gray70", 
      col="black")
lines(MC1_T4.5$Buckley, MC1_T4.5$qPCR_RMAX,type="o", pch=23, bg="gray70", 
      col="black")
legend("topright", legend=c("MC1-C12-T2.5", "MC1-C12-T3.5","MC1-C12-T3.5"), pch=c(21,22,23),
       pt.bg="gray70", bty='n')

plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected", xlim=c(1.7, 1.83),ylim=c(0,20),
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21)
lines(MC1_T3.5$Corrected, MC1_T3.5$qPCR_conc,type="o", pch=22, bg="gray70", 
      col="black")
lines(MC1_T4.5$Corrected, MC1_T4.5$qPCR_conc,type="o", pch=23, bg="gray70", 
      col="black")
legend("topright", legend=c("MC1-C12-T2.5", "MC1-C12-T3.5", "MC1-C12-T4.5"), pch=c(21,22,23),
       pt.bg="gray70", bty='n')

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley", xlim=c(1.73, 1.85),
     ylim=c(0,20),
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21)
lines(MC1_T3.5$Buckley, MC1_T3.5$qPCR_conc,type="o", pch=22, bg="gray70", 
      col="black")
lines(MC1_T4.5$Buckley, MC1_T4.5$qPCR_conc,type="o", pch=23, bg="gray70", 
      col="black")
legend("topright", legend=c("MC1-C12-T2.5", "MC1-C12-T3.5","MC1-C12-T3.5"), pch=c(21,22,23),
       pt.bg="gray70", bty='n')

}
```
#### T2.5


##### MC1-C12 vs. MC2-Met
```{r qpcr_1, fig.height=7,fig.width=8, dpi=300}

read=read.csv('/Users/oliviaahern/Documents/R/Exp4/25Aug22/qpcr_30Aug22.csv',header=T)

MC2_T2.5=subset(read, read$MC=="MC2" & TP =="2.5")
MC2_T3.5=subset(read, read$MC=="MC2" & TP =="3.5")
MC2_T4.5=subset(read, read$MC=="MC2" & TP =="4.5")
MC1_T4.5=subset(read, read$MC=="MC1" & TP == "4.5")
MC1_T2.5=subset(read, read$MC=="MC1" & TP == "2.5")
MC1_T3.5=subset(read, read$MC=="MC1" & TP == "3.5")
MC3_T2.5=subset(read, read$MC=="MC3" & TP =="2.5")
MC3_T3.5=subset(read, read$MC=="MC3" & TP =="3.5")
MC3_T4.5=subset(read, read$MC=="MC3" & TP =="4.5")
MC4_T2.5=subset(read, read$MC=="MC4" & TP =="2.5")
MC4_T3.5=subset(read, read$MC=="MC4" & TP =="3.5")
MC4_T4.5=subset(read, read$MC=="MC4" & TP =="4.5")
MC5_T2.5=subset(read, read$MC=="MC5" & TP =="2.5")
MC5_T3.5=subset(read, read$MC=="MC5" & TP =="3.5")
MC5_T4.5=subset(read, read$MC=="MC5" & TP =="4.5")
MC6_T2.5=subset(read, read$MC=="MC6" & TP =="2.5")
MC6_T3.5=subset(read, read$MC=="MC6" & TP =="3.5")
MC6_T4.5=subset(read, read$MC=="MC6" & TP =="4.5")



{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC2_T2.5$Corrected, MC2_T2.5$qPCR_RMAX,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC2_T2.5$Buckley, MC2_T2.5$qPCR_RMAX,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.735,1.85),
     ylim=c(0.00001,175))
lines(MC2_T2.5$Corrected, MC2_T2.5$qPCR_conc,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.735,1.85),
     ylim=c(0.00001,175))
lines(MC2_T2.5$Buckley, MC2_T2.5$qPCR_conc,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T2.5", "MC2-Met-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')
}
```


##### MC1-C12 vs. MC3-Eth

```{r qpcr_2, fig.height=7,fig.width=8, dpi=300}
{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC3_T2.5$Corrected, MC3_T2.5$qPCR_RMAX,type="o", pch=22, bg="#6870c8", 
      col="#6870c8")
legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#6870c8"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC3_T2.5$Buckley, MC3_T2.5$qPCR_RMAX,type="o", pch=22, bg="#6870c8", 
      col="#6870c8")
legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#6870c8"), bty='n', cex=0.9)


plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.735,1.85),
     ylim=c(0,230))
lines(MC3_T2.5$Corrected, MC3_T2.5$qPCR_conc,type="o", pch=22, bg="#6870c8", 
      col="#6870c8")
legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#6870c8"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.735,1.85),
     ylim=c(0,230))
lines(MC3_T2.5$Buckley, MC3_T2.5$qPCR_conc,type="o", pch=22, bg="#6870c8", 
      col="#6870c8")
legend("topright", legend=c("MC1-C12-T2.5", "MC3-Eth-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#6870c8"), bty='n', cex=0.9)
}
```


##### MC1-C12 vs. MC4-Ace
```{r qpcr_3, fig.height=7,fig.width=8, dpi=300}
{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC4_T2.5$Corrected, MC4_T2.5$qPCR_RMAX,type="o", pch=22, bg="#56ae6c", 
      col="#56ae6c")
legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#56ae6c"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC4_T2.5$Buckley, MC4_T2.5$qPCR_RMAX,type="o", pch=22, bg="#56ae6c", 
      col="#56ae6c")
legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#56ae6c"), bty='n', cex=0.9)

plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC4_T2.5$Corrected, MC4_T2.5$qPCR_conc,type="o", pch=22, bg="#56ae6c", 
      col="#56ae6c")
legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#56ae6c"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC4_T2.5$Buckley, MC4_T2.5$qPCR_conc,type="o", pch=22, bg="#56ae6c", 
      col="#56ae6c")
legend("topright", legend=c("MC1-C12-T2.5", "MC4-Ace-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#56ae6c"), bty='n', cex=0.9)
}
```


##### MC1 vs. MC5 - Redo Spin

REDO SPIN

```{r qpcr_4, fig.height=7,fig.width=8, dpi=300}
{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC5_T2.5$Corrected, MC5_T2.5$qPCR_RMAX,type="o", pch=22, bg="#af953c", 
      col="#af953c")
legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC5_T2.5$Buckley, MC5_T2.5$qPCR_RMAX,type="o", pch=22, bg="#af953c", 
      col="#af953c")
legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)


plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.735,1.85),
     ylim=c(0,7.25))
lines(MC5_T2.5$Corrected, MC5_T2.5$qPCR_conc,type="o", pch=22, bg="#af953c", 
      col="#af953c")
legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, xlim=c(1.735,1.85),
     ylim=c(0,7.25))
lines(MC5_T2.5$Buckley, MC5_T2.5$qPCR_conc,type="o", pch=22, bg="#af953c", 
      col="#af953c")
legend("topright", legend=c("MC1-C12-T2.5", "MC5-Glu-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)
}
```



##### MC1 vs. MC6 - Redo Spin 
REDO SPIN
```{r qpcr_5, fig.height=7,fig.width=8, dpi=300}
{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC6_T2.5$Corrected, MC6_T2.5$qPCR_RMAX,type="o", pch=22, bg="#ba4a4f", 
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85))
lines(MC6_T2.5$Buckley, MC6_T2.5$qPCR_RMAX,type="o", pch=22, bg="#ba4a4f", 
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)

plot(MC1_T2.5$Corrected, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85),
     ylim=c(0, 40))
lines(MC6_T2.5$Corrected, MC6_T2.5$qPCR_conc,type="o", pch=22, bg="#ba4a4f", 
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)

plot(MC1_T2.5$Buckley, MC1_T2.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21, xlim=c(1.735,1.85),
     ylim=c(0, 40))
lines(MC6_T2.5$Buckley, MC6_T2.5$qPCR_conc,type="o", pch=22, bg="#ba4a4f", 
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T2.5", "MC6-Xyl-T2.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)
}
```


#### T3.5 - redo C12 qRT PCR

##### MC1-C12 vs. MC2-Met -Redo qRT PCR

```{r qpcr_1a, fig.height=7,fig.width=8, dpi=300}

read=read.csv('/Users/oliviaahern/Documents/R/Exp4/25Aug22/qpcr_1Sept22.csv',header=T)

MC2_T2.5=subset(read, read$MC=="MC2" & TP =="2.5")
MC2_T3.5=subset(read, read$MC=="MC2" & TP =="3.5")
MC2_T4.5=subset(read, read$MC=="MC2" & TP =="4.5")
MC1_T4.5=subset(read, read$MC=="MC1" & TP == "4.5")
MC1_T2.5=subset(read, read$MC=="MC1" & TP == "2.5")
MC1_T3.5=subset(read, read$MC=="MC1" & TP == "3.5")
MC3_T2.5=subset(read, read$MC=="MC3" & TP =="2.5")
MC3_T3.5=subset(read, read$MC=="MC3" & TP =="3.5")
MC3_T4.5=subset(read, read$MC=="MC3" & TP =="4.5")
MC4_T2.5=subset(read, read$MC=="MC4" & TP =="2.5")
MC4_T3.5=subset(read, read$MC=="MC4" & TP =="3.5")
MC4_T4.5=subset(read, read$MC=="MC4" & TP =="4.5")
MC5_T2.5=subset(read, read$MC=="MC5" & TP =="2.5")
MC5_T3.5=subset(read, read$MC=="MC5" & TP =="3.5")
MC5_T4.5=subset(read, read$MC=="MC5" & TP =="4.5")
MC6_T2.5=subset(read, read$MC=="MC6" & TP =="2.5")
MC6_T3.5=subset(read, read$MC=="MC6" & TP =="3.5")
MC6_T4.5=subset(read, read$MC=="MC6" & TP =="4.5")



{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc", bg='gray70',pch=21)
lines(MC2_T3.5$Corrected, MC2_T3.5$qPCR_RMAX,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc", bg='gray70',pch=21)
lines(MC2_T3.5$Buckley, MC2_T3.5$qPCR_RMAX,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, 
     ylim=c(0.00001,20))
lines(MC2_T3.5$Corrected, MC2_T3.5$qPCR_conc,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, 
     ylim=c(0.00001,20))
lines(MC2_T3.5$Buckley, MC2_T3.5$qPCR_conc,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T3.5", "MC2-Met-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')
}
```




##### MC1 vs. MC3 - Redo Spin

```{r qpcr_2a, fig.height=7,fig.width=8,dpi=300}
{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)
lines(MC3_T3.5$Corrected, MC3_T3.5$qPCR_RMAX,type="o", pch=22, bg="#6870c8", 
      col="#6870c8")
legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#6870c8"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)
lines(MC3_T3.5$Buckley, MC3_T3.5$qPCR_RMAX,type="o", pch=22, bg="#6870c8", 
      col="#6870c8")
legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#6870c8"), bty='n', cex=0.9)


plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21,
     ylim=c(0,20))
lines(MC3_T3.5$Corrected, MC3_T3.5$qPCR_conc,type="o", pch=22, bg="#6870c8", 
      col="#6870c8")
legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#6870c8"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, 
     ylim=c(0,20))
lines(MC3_T3.5$Buckley, MC3_T3.5$qPCR_conc,type="o", pch=22, bg="#6870c8", 
      col="#6870c8")
legend("topright", legend=c("MC1-C12-T3.5", "MC3-Eth-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#6870c8"), bty='n', cex=0.9)
}
```




##### MC1-C12 vs. MC4-Ace
```{r qpcr_3a, fig.height=7,fig.width=8, dpi=300}
{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)
lines(MC4_T3.5$Corrected, MC4_T3.5$qPCR_RMAX,type="o", pch=22, bg="#56ae6c", 
      col="#56ae6c")
legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#56ae6c"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)
lines(MC4_T3.5$Buckley, MC4_T3.5$qPCR_RMAX,type="o", pch=22, bg="#56ae6c", 
      col="#56ae6c")
legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#56ae6c"), bty='n', cex=0.9)

plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21)
lines(MC4_T3.5$Corrected, MC4_T3.5$qPCR_conc,type="o", pch=22, bg="#56ae6c", 
      col="#56ae6c")
legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#56ae6c"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21)
lines(MC4_T3.5$Buckley, MC4_T3.5$qPCR_conc,type="o", pch=22, bg="#56ae6c", 
      col="#56ae6c")
legend("topright", legend=c("MC1-C12-T3.5", "MC4-Ace-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#56ae6c"), bty='n', cex=0.9)
}
```


##### MC1-C12 vs. MC5-Glu - Redo qRT PCR

```{r qpcr_4a, fig.height=7,fig.width=8, dpi=300}
{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)
lines(MC5_T3.5$Corrected, MC5_T3.5$qPCR_RMAX,type="o", pch=22, bg="#af953c", 
      col="#af953c")
legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)
lines(MC5_T3.5$Buckley, MC5_T3.5$qPCR_RMAX,type="o", pch=22, bg="#af953c", col="#af953c")
legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)

plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21)
lines(MC5_T3.5$Corrected, MC5_T3.5$qPCR_conc,type="o", pch=22, bg="#af953c", 
      col="#af953c")
legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21)
lines(MC5_T3.5$Buckley, MC5_T3.5$qPCR_conc,type="o", pch=22, bg="#af953c", 
      col="#af953c")
legend("topright", legend=c("MC1-C12-T3.5", "MC5-Glu-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#af953c"), bty='n', cex=0.9)
}
```



##### MC1-C12 vs. MC6-Xyl - redo qRT PCR

```{r qpcr_5a, fig.height=7,fig.width=8, dpi=300}
{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)
lines(MC6_T3.5$Corrected, MC6_T3.5$qPCR_RMAX,type="o", pch=22, bg="#ba4a4f", 
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)
lines(MC6_T3.5$Buckley, MC6_T3.5$qPCR_RMAX,type="o", pch=22, bg="#ba4a4f", 
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)

plot(MC1_T3.5$Corrected, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)

lines(MC6_T3.5$Corrected, MC6_T3.5$qPCR_conc,type="o", pch=22, bg="#ba4a4f", 
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)

plot(MC1_T3.5$Buckley, MC1_T3.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc.", bg='gray70',pch=21)
lines(MC6_T3.5$Buckley, MC6_T3.5$qPCR_conc,type="o", pch=22, bg="#ba4a4f", 
      col="#ba4a4f")
legend("topright", legend=c("MC1-C12-T3.5", "MC6-Xyl-T3.5"), pch=c(21,21),
       pt.bg=c("gray70", "#ba4a4f"), bty='n', cex=0.9)
}
```



#### T4.5 

##### MC1-C12 vs. MC2-Met - redo qRT PCR

```{r qpcr_1c, fig.height=7,fig.width=8, dpi=300}


{
par(mfrow=c(2,2), mar=c(5,5,1,1))
plot(MC1_T4.5$Corrected, MC1_T4.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="Normalized RNA Conc", bg='gray70',pch=21)
lines(MC2_T4.5$Corrected, MC2_T4.5$qPCR_RMAX,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T4.5$Buckley, MC1_T4.5$qPCR_RMAX,type="o", xlab="Buoyant Density - Buckley",
     ylab="Normalized RNA Conc", bg='gray70',pch=21)
lines(MC2_T4.5$Buckley, MC2_T4.5$qPCR_RMAX,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T4.5$Corrected, MC1_T4.5$qPCR_conc,type="o", xlab="Buoyant Density - Lueders Corrected",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21, 
     ylim=c(0.00001,10))
lines(MC2_T4.5$Corrected, MC2_T4.5$qPCR_conc,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')

plot(MC1_T4.5$Buckley, MC1_T4.5$qPCR_conc,type="o", xlab="Buoyant Density - Buckley",
     ylab="RNA Conc. (ng/uL)", bg='gray70',pch=21,
     ylim=c(0.00001,10))
lines(MC2_T4.5$Buckley, MC2_T4.5$qPCR_conc,type="o", pch=21, bg="#a44f9a", 
      col="#a44f9a")
legend("topright", legend=c("MC1-C12-T4.5", "MC2-Met-T4.5"), pch=c(21,21),
       pt.bg=c("gray70", "#a44f9a"), bty='n')
}
```

# 16S Community Data

```{r}
library(phyloseq)
x<-read.csv(file='/Users/oliviaahern/Documents/MBL_WHOI/Trophic_Cascades/Experiment4/Sequences/asv-table.csv',header=TRUE,row.names=1)
OTU = otu_table(x, taxa_are_rows=T)
taxa<-read.csv(file="/Users/oliviaahern/Documents/MBL_WHOI/Trophic_Cascades/Experiment4/Sequences/taxonomy.csv",header=TRUE,row.names=1)
t<-as.matrix(taxa)
tax2<-tax_table(t)
map<-import_qiime_sample_data("/Users/oliviaahern/Documents/MBL_WHOI/Trophic_Cascades/Experiment4/Sequences/map_exp4.txt")
phyo = phyloseq(OTU, tax2,map)
phyo
phyo1 = subset_taxa(phyo, !Order=="Chloroplast")
phyo2 = subset_taxa(phyo1, !Family=="Mitochondria")
phyo=phyo2
phyo
```


## PCoA with Pond 

Transform data - remove ASVs that are less than 0.01% of total dataset and minimum reads of 2. 
Aitchinson's distance - Euclidean distance of centered log ratio data. 


```{r pcoa_all_samples,fig.height=5,fig.width=8, dpi=300}

library(CoDaSeq)
library(compositions)
input=t(data.frame(otu_table(phyo)))
dim(input)
d.subset <- codaSeq.filter(input, 
                           samples.by.row=T,min.reads=2,min.prop =0.0001)

dim(d.subset)
log_rats <- (compositions::clr(t(d.subset)))
OTU=otu_table(t(log_rats),taxa_are_rows = T)
comp_clr=phyloseq(OTU,map,tax2)


otu=t(otu_table(comp_clr))
euc=vegdist(otu,'euc')
p=prcomp(euc)
# summary(p)
{
par(mar=c(7,8,1,10))
plot(p$x[,1],p$x[,2], pch = sample_data(comp_clr)$pch,
     bg=sample_data(comp_clr)$col,cex.lab=1.3,
     xlab= 'PCoA1 62.10%', ylab='PCoA2 13.71%',cex=1.5)
legend(60,60, legend=c("MC1-C12 Batch","MC1-C12 Chemostat",
                            "MC2-Met Batch", "MC2-Met Chemostat",
                            "MC3-Eth Batch", "MC3-Eth Chemostat",
                            "MC4-Ace Batch", "MC4-Ace Chemostat",
                            "MC5-Glu Batch", "MC5-Glu Chemostat",
                            "MC6-Xyl Batch", "MC6-Xyl Chemostat",
                            "Pond"),xpd=T,
       pt.bg=c("gray70","gray70","#a44f9a","#a44f9a","#6870c8","#6870c8",
             "#56ae6c","#56ae6c","#af953c","#af953c","#ba4a4f","#ba4a4f",
             "black"),
       pch=c(21,23,21,23,21,23,21,23,21,23,21,23, 24),
       bty='n',cex=1)
ordiellipse(p, groups=sample_data(comp_clr)$Timepoint)
}
```

## PCoA no Pond
Transform data - remove ASVs that are less than 0.01% of total dataset and minimum reads of 2. 
Aitchinson's distance - Euclidean distance of centered log ratio data. 

```{r pcoa_nopond,fig.height=5,fig.width=8, dpi=300}
data1=subset_samples(phyo, Treatment !="Pond")
input=t(data.frame(otu_table(data1)))
dim(input)
d.subset <- codaSeq.filter(input, 
                           samples.by.row=T,min.reads=2,min.prop =0.0001)

dim(d.subset)
log_rats <- (compositions::clr(t(d.subset)))
OTU=otu_table(t(log_rats),taxa_are_rows = T)
comp_clr=phyloseq(OTU,map,tax2)


otu=t(otu_table(comp_clr))
euc=vegdist(otu,'euc')
p=prcomp(otu)
#summary(p)
{
par(mar=c(7,8,1,10))
plot(p$x[,1],p$x[,2], pch = sample_data(data1)$pch,
     bg=sample_data(data1)$col,cex.lab=1.3,
     xlab= 'PCoA1 29.17%', ylab='PCoA2 11.24%',cex=1.5)
legend(12,20, legend=c("MC1-C12 Batch","MC1-C12 Chemostat",
                            "MC2-Met Batch", "MC2-Met Chemostat",
                            "MC3-Eth Batch", "MC3-Eth Chemostat",
                            "MC4-Ace Batch", "MC4-Ace Chemostat",
                            "MC5-Glu Batch", "MC5-Glu Chemostat",
                            "MC6-Xyl Batch", "MC6-Xyl Chemostat"),xpd=T,
       pt.bg=c("gray70","gray70","#a44f9a","#a44f9a","#6870c8","#6870c8",
             "#56ae6c","#56ae6c","#af953c","#af953c","#ba4a4f","#ba4a4f"),
       pch=c(21,23,21,23,21,23,21,23,21,23,21,23),
       bty='n',cex=1)
ordiellipse(p, groups=sample_data(comp_clr)$Timepoint)
}

```